---
format: 
  html:
    css: styles.css
    toc: false
page-layout: full
include-in-header: script.js

---
``` {r, echo=FALSE, results='asis'}
# List image files in the folder
image_files <- list.files("img/communityCodingImages", pattern = "\\.(jpg|jpeg|png|gif)$", ignore.case = TRUE, full.names = TRUE)

image_tags <- paste(
  sapply(seq_along(image_files), function(i) {
    img <- image_files[i]
    class <- if (i == 1) 'carousel-item active' else 'carousel-item'
    paste0('<div class="', class, '"><img src="', img, '" alt="Image"></div>')
  }),
  collapse = "\n"
)
```

:::: {.layout-container}

::: {.welcome-section}

# Community Coding

Got data and working on analysis? Got questions on using R, Python or other programming languages? Come and hang out with other coders in a welcoming and supportive environment.

Students, staff, faculty, and the public are invited to join our Community Coding sessions. Bring your computer, coding projects, and questions to this open working environment.

:::

:::{.carousel}
::: {.carousel-inner}
`r image_tags`
:::

<!-- Carousel Controls -->
<button class="carousel-control prev" onclick="prevSlide()">&#10094;</button>
<button class="carousel-control next" onclick="nextSlide()">&#10095;</button>
:::

::::

:::{.text-section}
```{r, echo=FALSE, results='asis'}
# Function to determine current semester
get_current_semester <- function() {
  current_date <- Sys.Date()
  month <- as.numeric(format(current_date, "%m"))
  year <- as.numeric(format(current_date, "%Y"))
  
  # Determine semester based on month
  if (month >= 1 && month <= 6) {
    semester <- "Spring"
  } else {
    semester <- "Fall"
  }
  
  paste(semester, year)
}

# Generate dynamic header
cat(paste("##", "Schedule & Locations for", get_current_semester()))
```

Community Coding is regularly held at The Innovation Lab on the second floor of the Meriam Library next to the print center. Additional drop in help sessions are available by individual faculty in their office or over Zoom. Please sign in at the link below to help us track attendance!
:::

<a href="https://docs.google.com/forms/d/e/1FAIpQLSfzHYqSO2DGD8ZPa_-q6JjpDi4AEcQDz2KyvgmtU1lWLSbORw/viewform " class="btn btn-primary" target="_blank" style="padding:10px 20px; text-decoration:none; background-color:9D2235#; color:#ffff; border-radius:5px;"> Sing In
</a>


:::{.calendar}
<!-- If you ever need to change where the calendar source is, simply get the embedded link and paste it after 'src=' -->
<iframe src="https://docs.google.com/spreadsheets/d/e/2PACX-1vRFeor7G0FO4mDM3EYZkO4-_F3fov_Z6si2ZT2Wwyxf87dJY3x0YqA14eY6X6q90Vcud637PF22G2ry/pubhtml?gid=0&amp;single=true&amp;widget=true&amp;headers=false" style="border: 0" width="75%" height="600" frameborder="0" scrolling="no"></iframe>
:::



